---
title: "Project Part 1: Part 1 - Exploration"
output: pdf_document
author: "Savannah McCoy"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(dbplyr)
library(doBy)
library(extrafont)
library(ggplot2)
library(reshape2)
library(hexbin)
```


## Project Part 1 - Exploration


# MODIFYING IS_POPULAR BOOLEAN LIMIT
```{r 1.1}

df <- read.csv("final_new_data.csv", sep=',')
df$is_popular <- ifelse(df$song_popularity >= 70, 1, 0)
df_pop <- subset(df, is_popular == 1) # 4541/139606 = 0.032527 = 3.25%

```


# CHOOSING A HOLDOUT SET 
```{r 1.2}
set.seed(1)

smp_size <- floor(0.71631 * nrow(df))
train_ind <- sample(seq_len(nrow(df)), size = smp_size)

df_train <- df[train_ind, ]
df_test <- df[-train_ind, ]

```



# PLOTTING Song Popularity Density
```{r 2.2}

plot_theme <- theme(
                    panel.background = element_rect(fill = "#575757",
                                                  colour = "#575757"),
                    panel.grid.major = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "black"),
                    panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "black"),
                    plot.title = element_text(hjust = 0.5, 
                                              family="Roboto Mono", 
                                              size = 12, 
                                              margin=margin(0,0,5,0)),
                    text = element_text(colour="white", 
                                        family="Roboto Mono", 
                                        size = 10),
                    axis.text = element_text(colour="white"),
                    plot.background = element_rect(fill = "black")
                    )


p <- ggplot(df_train, aes(x=song_popularity)) + 
            geom_density(fill="#42db00",) +
            plot_theme



# Add mean line
g <- p + geom_vline(aes(xintercept=mean(x=song_popularity)), 
                    color="#f673a2", 
                    linetype="dashed", 
                    alpha=1,
                    size=1)

ggsave("plot1.png", plot = g, width = 6, height = 4, dpi = 300, units = "in", device='png')

```



# PLOTTING Median & mean Song Popularity
```{r 2.3}

plot_theme <- theme(
                    panel.background = element_rect(fill = "#575757",
                                                  colour = "#575757"),
                    panel.grid.major = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "black"),
                    panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "black"),
                    plot.title = element_text(hjust = 0.5, 
                                              family="Roboto Mono", 
                                              size = 12, 
                                              margin=margin(0,0,5,0)),
                    text = element_text(colour="white", 
                                        family="Roboto Mono", 
                                        size = 10),
                    axis.text = element_text(colour="white"),
                    plot.background = element_rect(fill = "black"),
                    legend.position="right",
                    legend.key = element_rect(fill = "transparent", colour = "transparent"),
                    legend.background = element_blank())


c <- summaryBy(song_popularity ~ year, data = df_train, FUN = list(mean, max, min, median, sd))
myvars <- c("song_popularity.mean", "song_popularity.median", "year")
d <- c[myvars]
dd <-  melt(d, id.vars="year")


m <- ggplot(dd, aes(year, value, col=variable)) + geom_line(size = 1.2) +
        labs(
           x = "Year",
           y = "Popularity Score") +
      scale_color_manual(labels = c("Mean", "Median"), values = c("#42db00", "#f7e22e")) +
      scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
      plot_theme

ggsave("plot2.png", plot = m, width = 6, height = 4, dpi = 300, units = "in", device='png')

```


# Distribution of Audio Features
```{r 5}

plot_theme <- theme(
                    panel.background = element_rect(fill = "#575757",
                                                  colour = "#575757"),
                    panel.grid.major = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "#575757"),
                    panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "#575757"),
                    plot.title = element_text(hjust = 0.5, 
                                              family="Roboto Mono", 
                                              size = 12, 
                                              margin=margin(0,0,5,0)),
                    text = element_text(colour="white", 
                                        family="Roboto Mono", 
                                        size = 5),
                    axis.text = element_text(colour="white"),
                    plot.background = element_rect(fill = "black")
                    )

df_train_sub2 <- subset(df_train, duration_ms < 1000000)
q <- ggplot(df_train_sub2, aes(x=duration_ms)) + geom_histogram(binwidth = 50000, fill="white",) + plot_theme

i <- ggplot(df_train, aes(x=time_signature)) + geom_histogram(binwidth = 0.1, fill="white",) + plot_theme
w <- ggplot(df_train, aes(x=key)) + geom_histogram(binwidth = 0.5, fill="white",) + plot_theme +
                      scale_x_continuous(breaks = scales::pretty_breaks(n = 11)) 

df_train_sub3 <- subset(df_train, instrumentalness <= 0.000005)
r <- ggplot(df_train_sub3, aes(x=instrumentalness)) + geom_density(fill="white", size = 0.1) + plot_theme

df_train_sub4 <- subset(df_train, speechiness <= 0.25)
s <- ggplot(df_train_sub4, aes(x=speechiness)) + geom_density(fill="white", size = 0.1) + plot_theme

t <- ggplot(df_train, aes(x=danceability)) + geom_density(fill="white", size = 0.1) + plot_theme

u <- ggplot(df_train, aes(x=loudness)) + geom_density(fill="white", size = 0.1) + plot_theme
v <- ggplot(df_train, aes(x=energy)) + geom_density(fill="white", size = 0.1) + plot_theme
x <- ggplot(df_train, aes(x=liveness)) + geom_density(fill="white", size = 0.1) + plot_theme

y <- ggplot(df_train, aes(x=tempo)) + geom_density(fill="white", size = 0.1) + plot_theme
z <- ggplot(df_train, aes(x=valence)) + geom_density(fill="white", size = 0.1) + plot_theme
h <- ggplot(df_train, aes(x=acousticness)) + geom_density(fill="white", size = 0.1) + plot_theme


gg <- ggarrange(r, s, q, i, v, x, t, h, y, z, u, w, 
                align = "v", ncol = 3, nrow = 4)

ggsave("plot3.png", plot = gg, width = 5, height = 3)

# print(q)
# print(i)
# print(w)
# print(r)
# print(s)
# print(t)
# print(u)
# print(v)
# print(x)
# print(y)
# print(z)
# print(h)

```


# Followers, Artist popularity distribution
```{r 3}
plot_theme <- theme(
                    panel.background = element_rect(fill = "#575757",
                                                  colour = "#575757"),
                    panel.grid.major = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "black"),
                    panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "black"),
                    plot.title = element_text(hjust = 0.5, 
                                              family="Roboto Mono", 
                                              size = 12, 
                                              margin=margin(0,0,5,0)),
                    text = element_text(colour="white", 
                                        family="Roboto Mono", 
                                        size = 8),
                    axis.text = element_text(colour="white"),
                    plot.background = element_rect(fill = "black"))

j <- ggplot(df_train, aes(x=primary_artist_popularity)) + 
  geom_histogram(binwidth=3, fill="greenyellow",color="black", size=0.5) + 
  plot_theme 


# k <- ggplot(df_train, aes(x=primary_artist_followers)) + 
#   geom_histogram(binwidth=300000,fill="greenyellow",color="black", size=0.25) +
#   scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
#   plot_theme 


# ggsave("plot7.png", plot = k, width = 8, height = 3)

print(k)

```

```{r 7.1}

k1 <- ggplot(df_train, aes(x=primary_artist_followers)) + 
  geom_histogram(binwidth=300000,fill="greenyellow",color="black", size=0.25) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  plot_theme1 

k2 <- ggplot(df_train_sub1, aes(x=primary_artist_followers)) + 
  geom_histogram(fill="greenyellow",color="black", size=0.25) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5)) +
  plot_theme1

gp2 <- ggarrange(k1, k2, align = "h", ncol = 2, nrow = 1)
ggsave("plot7-1.png", plot = gp2, width = 8, height = 3)

```


```{r 8}

l <- ggplot(df_train, aes(x=primary_artist_popularity)) + 
            geom_density(fill="lightgreen",) +
            plot_theme +
            geom_vline(aes(xintercept=mean(x=primary_artist_popularity)), 
                    color="#ffcdd4", 
                    linetype="dashed", 
                    alpha=1,
                    size=1)

print(l)
gp <- ggarrange(g, l, align = "h", ncol = 2, nrow = 1)
ggsave("plot8.png", plot = gp, width = 8, height = 3)

```

# - Number of popular songs (by year)
```{r 7}
# df_train_sub <- subset(df_train, is_popular == 1)
# oo <- count(df_train_sub, "year")
# o <-ggplot(data=oo, aes(x=year, y=freq)) + 
#   geom_bar(stat="identity", fill='violetred', color="black", size=0.25) + 
#   plot_theme +
#   scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
#   labs(x = "Year",
#        y = "Count")
# ggsave("plot9-1.png", plot = o, width = 7, height = 3)
```


## Correlations between features -- scatterplots for pairs of covariates -  Grouped based on the level of a categorical variable
```{r 4}


plot_theme1 <- theme(
                    panel.background = element_rect(fill = "#575757",
                                                  colour = "#575757"),
                    panel.grid.major = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "black"),
                    panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "black"),
                    plot.title = element_text(hjust = 0.5,
                                              family="Roboto Mono",
                                              size = 9,
                                              margin=margin(0,0,5,0)),
                    text = element_text(colour="white",
                                        family="Roboto Mono",
                                        size = 8),
                    axis.text = element_text(colour="white"),
                    plot.background = element_rect(fill = "black"),
                    legend.position="right",
                    legend.key = element_rect(fill = "transparent", colour = "transparent"),
                    legend.background = element_blank())

plot_theme2 <- theme(
                    panel.background = element_rect(fill = "#575757",
                                                  colour = "#575757"),
                    panel.grid.major = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "transparent"),
                    panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                                  colour = "transparent"),
                    plot.title = element_text(hjust = 0.5,
                                              family="Roboto Mono",
                                              size = 10,
                                              margin=margin(0,0,5,0)),
                    text = element_text(colour="white",
                                        family="Roboto Mono",
                                        size = 10),
                    axis.text = element_text(colour="white"),
                    plot.background = element_rect(fill = "black"),
                    legend.position="right",
                    legend.key = element_rect(fill = "transparent", colour = "transparent"),
                    legend.background = element_blank())

```



```{r 4.1}
a1a <- ggplot(df_train, aes(x=song_popularity, y=primary_artist_popularity, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#34eb74','white'), name = "is Single?", labels = c("No", "Yes"))

a1b <- ggplot(df_train, aes(x=song_popularity, y=primary_artist_popularity, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#34eb74','white'), name = "Has feature?", labels = c("No", "Yes"))

a1c <- ggplot(df_train, aes(x=song_popularity, y=primary_artist_popularity, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#34eb74','white'), name = "is Explicit?", labels = c("No", "Yes"))

a1d <- ggplot(df_train, aes(x=song_popularity, y=primary_artist_popularity, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#34eb74','white'), name = "Mode")

a1e <- ggplot(df_train, aes(x=song_popularity, y=primary_artist_popularity)) + geom_hex() + plot_theme2 +
              scale_fill_gradient(limits=c(0,1000), breaks=seq(0, 1000, by=500), low = "#575757", high = "#34eb74")


ggp <- ggarrange(a1e, ggarrange(a1a, a1b, a1c, a1d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-1.png", plot = ggp, width = 8, height = 12, bg = "transparent")

```


# PRIMARY ARTIST FOLLOWERS
```{r 4.2}

df_train_sub1 <- subset(df_train, primary_artist_followers <= 5000000)

a2a <- ggplot(df_train_sub1, aes(x=song_popularity, y=primary_artist_followers, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#fcba03','white'), name = "is Single?", labels = c("No", "Yes"))


a2b <- ggplot(df_train_sub1, aes(x=song_popularity, y=primary_artist_followers, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#fcba03','white'), name = "Has feature?", labels = c("No", "Yes"))


a2c <- ggplot(df_train_sub1, aes(x=song_popularity, y=primary_artist_followers, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#fcba03','white'), name = "is Explicit?", labels = c("No", "Yes"))


a2d <- ggplot(df_train_sub1, aes(x=song_popularity, y=primary_artist_followers, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#fcba03','white'), name = "Mode")


k <- ggplot(df_train_sub1, aes(x=primary_artist_followers)) +
  geom_histogram(fill="greenyellow",color="black", size=0.25) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  plot_theme1

a2e <- ggplot(df_train_sub1, aes(x=song_popularity, y=primary_artist_followers)) + geom_hex() + plot_theme2 +
              scale_fill_gradient(limits=c(0,2000), breaks=seq(0, 5000, by=1000), low = "#575757", high = "#fcba03")


ggp <- ggarrange(a2e, ggarrange(a2a, a2b, a2c, a2d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-2.png", plot = ggp, width = 8, height = 12, bg = "transparent")

```


# DANCEABILITY
```{r 4.3}
a3a <- ggplot(df_train, aes(x=song_popularity, y=danceability, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#ff00aa','white'), name = "is Single?", labels = c("No", "Yes"))


a3b <- ggplot(df_train, aes(x=song_popularity, y=danceability, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#ff00aa','white'), name = "Has feature?", labels = c("No", "Yes"))


a3c <- ggplot(df_train, aes(x=song_popularity, y=danceability, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#ff00aa','white'), name = "is Explicit?", labels = c("No", "Yes"))


a3d <- ggplot(df_train, aes(x=song_popularity, y=danceability, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#ff00aa','white'), name = "Mode")


a3e <- ggplot(df_train, aes(x=song_popularity, y=danceability)) + geom_hex() + plot_theme2 +
              scale_fill_gradient(limits=c(0,600), breaks=seq(0, 500, by=100), low = "#575757", high = "#ff00aa")


ggp <- ggarrange(a3e, ggarrange(a3a, a3b, a3c, a3d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-3.png", plot = ggp, width = 8, height = 12, bg = "transparent")


```


# DURATION
```{r 4.4}

# CLIP LONG SONGS
df_train_sub2 <- subset(df_train, duration_ms < 1000000)
a4a <- ggplot(df_train_sub2, aes(x=song_popularity, y=duration_ms, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#c861ff','white'), name = "is Single?", labels = c("No", "Yes"))


a4b <- ggplot(df_train_sub2, aes(x=song_popularity, y=duration_ms, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#c861ff','white'), name = "Has feature?", labels = c("No", "Yes"))


a4c <- ggplot(df_train_sub2, aes(x=song_popularity, y=duration_ms, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#c861ff','white'), name = "is Explicit?", labels = c("No", "Yes"))


a4d <- ggplot(df_train_sub2, aes(x=song_popularity, y=duration_ms, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#c861ff','white'), name = "Mode")


a4e <- ggplot(df_train_sub2, aes(x=song_popularity, y=duration_ms)) + geom_hex() + plot_theme2 +
              scale_fill_gradient(limits=c(0,1500), breaks=seq(0, 1500, by=500), low = "#575757", high = "#c861ff")


ggp <- ggarrange(a4e, ggarrange(a4a, a4b, a4c, a4d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-4.png", plot = ggp, width = 8, height = 12, bg = "transparent")
```


# LOUDNESS
```{r 4.5}
a8a <- ggplot(df_train, aes(x=song_popularity, y=loudness, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#fcba03','white'), name = "is Single?", labels = c("No", "Yes"))


a8b <- ggplot(df_train, aes(x=song_popularity, y=loudness, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#fcba03','white'), name = "Has feature?", labels = c("No", "Yes"))


a8c <- ggplot(df_train, aes(x=song_popularity, y=loudness, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#fcba03','white'), name = "is Explicit?", labels = c("No", "Yes"))


a8d <- ggplot(df_train, aes(x=song_popularity, y=loudness, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#fcba03','white'), name = "Mode")


a8e <- ggplot(df_train, aes(x=song_popularity, y=loudness)) + geom_hex() + plot_theme2 +
              scale_fill_gradient(limits=c(0,1500), breaks=seq(0, 1500, by=500), low = "#575757", high = "#fcba03")


ggp <- ggarrange(a8e, ggarrange(a8a, a8b, a8c, a8d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-5.png", plot = ggp, width = 8, height = 12, bg = "transparent")



```


# LIVENESS
```{r 4.6}
a9a <- ggplot(df_train, aes(x=song_popularity, y=liveness, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "is Single?", labels = c("No", "Yes"))


a9b <- ggplot(df_train, aes(x=song_popularity, y=liveness, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "Has feature?", labels = c("No", "Yes"))


a9c <- ggplot(df_train, aes(x=song_popularity, y=liveness, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "is Explicit?", labels = c("No", "Yes"))


a9d <- ggplot(df_train, aes(x=song_popularity, y=liveness, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "Mode")


a9e <- ggplot(df_train, aes(x=song_popularity, y=liveness)) + geom_hex() + plot_theme2+
              scale_fill_gradient(limits=c(0,2000), breaks=seq(0, 2000, by=500), low = "#575757", high = "#bbff00")


ggp <- ggarrange(a9e, ggarrange(a9a, a9b, a9c, a9d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-6.png", plot = ggp, width = 8, height = 12, bg = "transparent")

```


# ENERGY
```{r 4.7}
a10a <- ggplot(df_train, aes(x=song_popularity, y=energy, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "is Single?", labels = c("No", "Yes"))


a10b <- ggplot(df_train, aes(x=song_popularity, y=energy, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "Has feature?", labels = c("No", "Yes"))


a10c <- ggplot(df_train, aes(x=song_popularity, y=energy, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "is Explicit?", labels = c("No", "Yes"))


a10d <- ggplot(df_train, aes(x=song_popularity, y=energy, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "Mode")


a10e <- ggplot(df_train, aes(x=song_popularity, y=energy)) + geom_hex() + plot_theme2 +
              scale_fill_gradient(limits=c(0,370), breaks=seq(0, 350, by=100), low = "#575757", high = "#bbff00")

ggp <- ggarrange(a10e, ggarrange(a10a, a10b, a10c, a10d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-7.png", plot = ggp, width = 8, height = 12, bg = "transparent")

```


# TEMPO
```{r 4.8}
a12a <- ggplot(df_train, aes(x=song_popularity, y=tempo, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#ff7ddc','white'), name = "is Single?", labels = c("No", "Yes"))


a12b <- ggplot(df_train, aes(x=song_popularity, y=tempo, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#ff7ddc','white'), name = "Has feature?", labels = c("No", "Yes"))


a12c <- ggplot(df_train, aes(x=song_popularity, y=tempo, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#ff7ddc','white'), name = "is Explicit?", labels = c("No", "Yes"))


a12d <- ggplot(df_train, aes(x=song_popularity, y=tempo, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#ff7ddc','white'), name = "Mode")


a12e <- ggplot(df_train, aes(x=song_popularity, y=tempo)) + geom_hex() + plot_theme2 +
              scale_fill_gradient(limits=c(0,800), breaks=seq(0, 800, by=200), low = "#575757", high = "#ff7ddc")

ggp <- ggarrange(a12e, ggarrange(a12a, a12b, a12c, a12d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-8.png", plot = ggp, width = 8, height = 12, bg = "transparent")


```


# SPEECHINESS
```{r 4.9}
a13a <- ggplot(df_train, aes(x=song_popularity, y=speechiness, color=as.factor(isSingle))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "is Single?", labels = c("No", "Yes"))


a13b <- ggplot(df_train, aes(x=song_popularity, y=speechiness, color=as.factor(hasFeature))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "Has feature?", labels = c("No", "Yes"))


a13c <- ggplot(df_train, aes(x=song_popularity, y=speechiness, color=as.factor(explicit))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "is Explicit?", labels = c("No", "Yes"))


a13d <- ggplot(df_train, aes(x=song_popularity, y=speechiness, color=as.factor(mode))) +
  geom_point(size=1, alpha=0.9) + plot_theme1 +
  scale_color_manual(values=c('#bbff00','white'), name = "Mode")


a13e <- ggplot(df_train, aes(x=song_popularity, y=speechiness)) + geom_hex() + plot_theme2 +
              scale_fill_gradient(limits=c(0,4000), breaks=seq(0, 4000, by=1000), low = "#575757", high = "#bbff00")

ggp <- ggarrange(a13e, ggarrange(a13a, a13b, a13c, a13d, align = "h", ncol = 2, nrow = 2) , align = "h", ncol = 1, nrow =2)
ggsave("plot4-9.png", plot = ggp, width = 8, height = 12, bg = "transparent")

```



